---
title: "Shiny App Pitch"
author: "C. Muhs"
date: "21 January 2018"
output: ioslides_presentation
transition: rotate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## State of the Union Addresses

The last three United States presidents have reputations in their word choices. George W Bush is known for simple word choices. Barack Obama is known as an inspiring and eloquent speaker. Donald Trump is known for having a raw, unfiltered vocabulary.

### Question

Would wordclouds from each of these presidents' State of the Union Addresses look different from one another?  

For this class project, I made a Shiny app to answer this question

## Process

- find the transcripts of each of these speeches
- use 'tm' package to mine the text files
- use 'wordcloud' package to create wordclouds
- configure shiny app to interact with the visualizations
- sample wordcloud from Obama's 2009 SOTU address:
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.align='right'}
library(tm)

obama_txt = readLines("https://raw.githubusercontent.com/cdmuhs/presidential_wordcloud/master/prez_wc/obama.txt")

toCorpus <- function(txt_file) {
    myCorpus = Corpus(VectorSource(txt_file))
    myCorpus = tm_map(myCorpus, tolower)
    myCorpus = tm_map(myCorpus, removePunctuation)
    myCorpus = tm_map(myCorpus, removeNumbers)
    myCorpus = tm_map(myCorpus, removeWords, stopwords("english"))
    myDTM = TermDocumentMatrix(myCorpus, control = list(minWordLength = 1))
    m = as.matrix(myDTM)
    v = sort(rowSums(m), decreasing = TRUE)
    return(v)    
}

# create wordcloud object for each president
# trumpCorpus <- toCorpus(trump_txt)
obamaCorpus <- toCorpus(obama_txt)
# bushCorpus <- toCorpus(bush_txt)

library(wordcloud)
set.seed(1234)
wordcloud(names(obamaCorpus), obamaCorpus, min.freq = 10)

```

## Shiny app contents

- instructions
- dropdown with three presidential addresses as options
- slider for word frequency in wordcloud
- slider for maximum number of words in wordcloud
- action button to generate wordcloud with input parameters
- wordcloud visualization

## Links

- [the github repository](https://github.com/cdmuhs/presidential_wordcloud)
- [the deployed shiny app](https://cdmuhs.shinyapps.io/prez_wc/)

### Thank you